High-Dim Project

### 2014-12-18 highdim-paper/paper.tex
Added 2.1 and 2.2

\documentclass[11pt]{article}
\usepackage{acl2014}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{graphicx}

@@

@@

>>>>

\documentclass[11pt]{article}
\usepackage{acl2014}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[]{algorithm2e}

@@

The task of multiclass classification involves the prediction of a class label
$l$ where the number of possible labels is $k>2$. More often than not, the 
original problem is transformed into $k$ binary classification problems, i.e.
$1$--vs.--all classification and positive prediction with the highest 
confidence is selected as the label. This approach has the disadvantage of
having to train $k$ different models.

An alternative formulation, direct multiclass classification, tackles this 
problem directly by solving the following $\operatorname{argmax}$ problem:
$$y_i = \operatorname{argmax}_c W_{:c}^T x_i $$
where $W \in \mathcal{R}^{p \times k}$ is a weight matrix, with $W_{ij}$
corresponding to the $i$-th feature of class $j$. In this paper, we refer
to features as elements in the instance data $x$. A feature in $x$ is
associated with $k$ weights in $W$, one for each class.

The decision function above suggests a max-margin style loss function. More
specifically, we use the squared hinge loss:

$$ l(W) = \sum_{i=1}^n \sum_{r\ne y_i}^k 
    \max\left(1 - (W_{:y_i}^Tx_i - W_{:r}^Tx_i), 0\right)^2 $$

The minimization of $l$ directly will lead to a minimizer $W^*$ that is
dense. Sparse solutions are often explicitly sought, with model compactness
leading to fast prediction at test time. In order to obtain a sparse $W^*$,
a regularization term $r(W)$ is often applied, yielding the objective 
function:

$$\min_W l(W) + r(W).$$

Many choices are available for the regularizer $r$. In (ref ???), they use
the group lasso, where each row in $W$ is a group. The associated regularizer 
then is $r(W) = \lambda\sum_j^p \|W_{j:}\|_2$ where $\lambda$ is a parameter
that adjusts the strength of the regularization.
This has the effect of producing a few rows of non-zero values in $W$;
since each row corresponds to an individual feature, the optimal sparse $W^*$
yields a fast-evaluating decision function, i.e. most features are 
ignored at test time.

To minimize this multiclass classification group lasso objective, ??? use 
coordiante descent, iteratively solving a sub-problem with respect to a 
single group. Figure ? shows a general outline of algorithm that involves
computing the partial gradient with respect to the 
current group $j$, the prox
operator of the L2 norm, and a final line search to identify an appropriate
step size for the current update.

\begin{algorithm}
 \For{$i \gets 1, \ldots, max\;iters $}{
     \For{$j \gets 1, \ldots, p$}{
        Compute gradient $l^\prime(W)_{j:}$\\
        Choose $\mathcal{L}_j$\\
        Compute \\
        $\;\;\;\;V_j = W_{j:} - \frac{1}{\mathcal{L}_j}l^\prime(W)_{j:}$\\
        $\;\;\;\;W_{j:}^* 
          = \operatorname{Prox}_{\frac{\lambda}{\mathcal{L}_j}\|\cdot\|_j}
         (V_j)$\\

         $\;\;\;\;\delta = W_{j:}^* - W_{j:}$\\
        Choose $\alpha$\\
        $W_{j:} \gets W_{j:} + \alpha \delta$\\

    }
 }
\end{algorithm}

Efficient computation of this objective is possible by storing current 
loss for each data point. Let $A$ be an $n\times k$ matrix where the 
$i,r$-th element corresponds to 
 $(1-(W_{:y_i}^Tx_i - W_{:r}x_i).$
 The gradient can then be calculated as 
 $l^\prime(W)_{j} = \frac{2}{n}\sum_{i=1}^n\sum_{r\ne y_i}
 \max(A_{ir}, 0)(x_{ij}e_{y_i} - x_{ij} e_r)$
where $e_r$ is a $k$ dimensional vector with zeroes everywhere except for a 1
at the $r$-th position. We only have to examine elements in $A$ for which 
the corresponding $x_{ij}$ is non-zero. When $x_{i}$ is sparse, more often
than not $x_{ij}$ is zero and can be ignored.

@@

One limitation of group lasso is that it assumes that group assignments are
non-overlapping. In some domains, this can be too restrictive an assumption.
For example, in document classification, individual words are used as features.
If we were to construct groupings of these features, we might run into a case
where one word could reasonably be added to several groups. The overlapping or
latent group lasso was introduced to handled such cases.

??? develop a theoretical justification for the latent group lasso, as well
as its equivalence to a regular group lasso in a higher dimensional space.
Let $\mathcal{G}$ be the set of (possibly overlapping) groups,
where $g \in \mathcal{G}$ is a set of indices of covariates associated with 
that group. 
Let our
data consist of vectors $x_i$ in $p$ dimensions, and let $w$ be the 
corresponding weight vector in $p$ dimensions that we would like to learn.
Finally, define $\operatorname{supp}(v)$ to be the support of $v$, i.e.
the indices of the non-zero elements in $v$.

For each group
$g \in \mathcal{G}$ we associate a latent vector $v^g \in \mathcal{R}^p$ where
$\operatorname{supp}(v^g) = g$, i.e. the nonzero elements in the $v^g$ correspond
to the indices in the group $g$. 
The original weight vector $w$ can be
interpreted as a sum of the latent vectors, or
$w = \sum_{g \in \mathcal{G}} v^g$. 
??? arrive at the following minimization
problem 
$$ \min_{w, v^g} l(w) + \lambda \sum_{g \in \mathcal{G}} d_g \|v^g \|_2 $$
$$\mathrm{s.t.}\;\;\; w = \sum_g v^g$$

??? show that when the original problem is regression, 
$w^Tx = \left(\sum_g v^g\right)^Tx = \hat{v}^T \hat{x}$ where 
$\hat{v} = (v^{g})_{g \in \mathcal{G}}$ and
$\hat{x} = \bigoplus_{g \in \mathcal{G} } (x_i)_{i \in g}$, i.e. $\hat{x}$ is
the restrictions of each $g$ stacked on top of each other. $\hat{x}, \hat{v}$ 
have dimension $\sum_{g \in \mathcal{G}} |g|$ 
In this formulation, the optimal $\hat{v}^*$ can be found using regular 
non-overlapping group lasso.
